Online {\IterComp}

### 2017-09-15 infra.tex
overall changes
infra agrees with figure 4

\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{figs/infra-diagram}
    \caption{Overview of the online \itercomp mechanism. \red{zw: mark the boundary of online and offline.}}
    \label{fig:infra-diagram}
\end{figure}

@@

This work focuses on the highlighted components of Figure~\ref{fig:infra-diagram}. The first one, \textit{Work Instrumentation} \blue{is
performed once at offline compile time}. It allows measuring the amount of work performed. Conceptually, we use the cost model of
Section~\ref{sec:metric} to estimate a cost for each basic block of the IR and then add instrumentation to increase a global work counter
by that cost every time a basic block is executed. The measured work should depend only on the program and the input, not the applied
optimizations, so we instrument the unoptimized IR before any optimizations modify it. We present a detailed description of work
instrumentation and how to keep it lightweight in Section~\ref{chap:instr}.

\textit{Optimization Selector} is responsible for selecting which optimization sequence to use for the next execution of the program. Each
sequence is used for multiple executions of the program in order to gather enough work efficiency measurements. When we are able to
estimate this work efficiency with a confidence interval narrower than a certain threshold, we can start evaluating a different
optimization sequence. We call the number of executions performed using the same optimization sequence the \textit{Input-Window Size}.

%\FIXME{WHAT IS THE OPTIMIZATION EVALUATOR? WHY IS IT HIGHLIGHTED? DO WE HAVE ANYTHING TO SAY ABOUT IT?}

>>>>

\begin{figure}[t]
    \centering
    \includegraphics[width=\linewidth]{figs/infra-diagram}
    \caption{Overview of the online \itercomp mechanism.}
    \label{fig:infra-diagram}
\end{figure}

@@

This work focuses on the highlighted component of Figure~\ref{fig:infra-diagram}, the \textit{Work Instrumentation}. It is performed once
and offline, right after the IR is generated. Its purpose is to measure the amount of work performed. Conceptually, we use the cost model of
Section~\ref{sec:metric} to estimate a cost for each basic block of the IR and then add instrumentation to increase a global work counter
by that cost every time a basic block is executed. The measured work represents the computational effort of the unoptimised program and it
should depend only on the program and the input, not the applied optimizations. For that reason, we instrument the unoptimized IR before any optimizations modify it. We present a detailed description of work
instrumentation and how to keep it lightweight in Section~\ref{sec:prof}.

Another component, the \textit{Search Driver}, is responsible for guiding the optimization process. Each selected optimization sequence
is used for multiple executions of the program in order to gather enough work efficiency measurements. When we are able to
estimate this work efficiency with a confidence interval narrower than a certain threshold, we can start evaluating a different
optimization sequence. We call the number of executions performed using the same optimization sequence the \textit{Input-Window Size}.
